Pairwise-complete correlation considered dangerous

### 2015-05-27 missing.Rmd
references

This note warns about potentially misleading results when using the
`use=pairwise.complete.obs` and `use=complete` options in R's `cor`
and `cov` functions. The note illustrates potential issues with
a very simple pathological example.

@@

* http://www.stat.columbia.edu/~gelman/arm/missing.pdf
* http://cran.r-project.org/web/packages/mi/
* http://gking.harvard.edu/amelia

>>>>

This note warns about potentially misleading results when using the
`use=pairwise.complete.obs` and related options in R's `cor`
and `cov` functions. The note illustrates potential issues using
a very simple pathological example and lists alternative approaches
to handling missing data and references about them.

@@

* http://www.stat.columbia.edu/~gelman/arm/missing.pdf
* http://cran.r-project.org/web/packages/mi/
* http://gking.harvard.edu/amelia
* http://cran.r-project.org/web/views/OfficialStatistics.html  (Look for the "Imputation" section in this task view for a list of R packages.)
